### 2024-03-09 docs/manuscript/manuscript.qmd
minor fix
minor change in citation

Main results are represented in the Figure X.

@@

As far as we know, there are not preceding studies addressing these findings. We posit that there exists further factors influencing the mediation effect. For instance, body distribution of the adipose tissue was not explored, specially when it is known that visceral fat has an important impact on cardiovascular health and its autonomic regulation [@pmid:31553779; pmid:32158768]. Participants with higher fitness may have a different fat distribution compared with lower performance individuals, which may induce different effects on autonomic drive to the heart [@pmid:19752873]. Furthermore, other physical physiological, demographic or psychological variables may be playing an unexplored role. However, these hypothesis must be examined under scientific standards. Therefore, exhaustive research is needed to address this intriguing interplay.

>>>>

@@

As far as we know, there are not preceding studies addressing these findings. We posit that there exists further factors influencing the mediation effect. For instance, body distribution of the adipose tissue was not explored, specially when it is known that visceral fat has an important impact on cardiovascular health and its autonomic regulation [@pmid:31553779; @pmid:32158768]. Participants with higher fitness may have a different fat distribution compared with lower performance individuals, which may induce different effects on autonomic drive to the heart [@pmid:19752873]. Furthermore, other physical physiological, demographic or psychological variables may be playing an unexplored role. However, these hypothesis must be examined under scientific standards. Therefore, exhaustive research is needed to address this intriguing interplay.
